% !TeX spellcheck = en_GB
\documentclass[a4paper, 12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{cancel}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{geometry}
\usepackage{lipsum}


%\usetikzlibrary{decorations.text}

\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{defin}[theorem]{Definition}
\newtheorem{cor}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{oss}[theorem]{Remark}
%
%\newtheorem{theor}{Teorema}[chapter]
%\newtheorem{lemma}[theor]{Lemma}
%\newtheorem{prop}[theor]{Proposizione}
%\newtheorem{coroll}[theor]{Corollario}

%
%\theoremstyle{definition}
%\newtheorem{defn}{Definizione}[chapter]
%\newtheorem{ex}{Esempio}[chapter]
%\newtheorem*{definizione-numr}{Definizione}
%
%\theoremstyle{remark}
%\newtheorem{oss}{Osservazione}[chapter]
%
%
%\newenvironment{skproof}{%
%	\renewcommand{\proofname}{Sketch di dimostrazione}\proof}{\endproof}
%\newenvironment{necproof}{%
%\renewcommand{\proofname}{Dimostrazione della necessarietà}\proof}{\endproof}
%\newenvironment{sufproof}{%
%\renewcommand{\proofname}{Dimostrazione della sufficienza}\proof}{\endproof}
%
\newcommand{\R}{\mathbb{R}}
\newcommand{\ttl}{THE ALEXANDROV MOVING PLANE METHOD \\AND APPLICATIONS TO GEOMETRIC FLOWS}

\author{Marco Tamburro \\ Relatore: Carlo Sinestrari}
\title{\ttl}
\date{\today}

\newenvironment{localsize}[1]
{%
	\clearpage
	\let\orignewcommand\newcommand
	\let\newcommand\renewcommand
	\makeatletter
	\input{size#1.clo}%
	\makeatother
	\let\newcommand\orignewcommand
}
{%
	\clearpage
}

\begin{document}

%\maketitle 
%\frontmatter
\begin{localsize}{11}
	\include{./TeX_files/frontespizio}
\end{localsize}
\tableofcontents

\phantomsection
\include{./TeX_files/introduzione}

%\mainmatter

\include{./TeX_files/chapter1}

\include{./TeX_files/chapter2}
\include{./TeX_files/chapter3}
\include{./TeX_files/chapter4}


\backmatter
% bibliography, glossary and index would go here.

\phantomsection

%\clearpage
\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{11} 
	\bibitem{Chow} Chow B.; {\em Geometric Aspects of Aleksandrov Reflection and Gradient Estimates for Parabolic Equations}, Communications in Analysis and Geometry, Volume 5, Number 2, 389-409, 1997.
	
	\bibitem{summary} Chow, B. (2023). {\em Aleksandrov reflection for extrinsic geometric flows of Euclidean hypersurfaces}. Advanced Nonlinear Studies, Vol. 23 (Issue 1), pp. 20220034.
	
	\bibitem{italiani} Ciraolo, G., Roncoroni, A., Vezzoni, L.;  {\em Quantitative stability for hypersurfaces with almost constant curvature in space forms}, Annali di Matematica 200, 2043–2083 (2021).
	
	\bibitem{symmetry hypersurfaces old}Levitt, G.; Rosenberg, H.. (1984). {\em Symmetry of Constant Mean Curvature Hypersurfaces in Hyperbolic Space}. Retrieved from the University Digital Conservancy.%, https://hdl.handle.net/11299/5011.
	
	\bibitem{SinestRisa} Sinestrari C., Risa S.; {\em Strong spherical rigidity of ancient solutions of expansive curvature flows},  Bull. London Math. Soc. 52, (2020) 94-99. 
	
	\bibitem{BryanIvakiScheuer}P. Bryan, M. N. Ivaki, and J. Scheuer, {\em On the Classification of Ancient Solutions to Curvature Flows on the Sphere}, 2017,
	arXiv:1604.01694v2.
	
	\bibitem{GidasNirenberg} Gidas B., Wei-Ming Ni, L.Nirenberg; {\em Symmetry and Related Properties via the Maximum Principle},  Commun. Math. Phys. 68, 209-243, 1979. 
	
	\bibitem{huisken} Gerhard, H., Alexander, P. (1999). {\em Geometric evolution equations for hypersurfaces.} In: Hildebrandt, S., Struwe, M. (eds) Calculus of Variations and Geometric Evolution Problems. Lecture Notes in Mathematics, vol 1713. Springer, Berlin, Heidelberg.
	
	\bibitem{volpres} Gerhard, H. {\em The volume preserving mean curvature flow.} Journal f\"{u}r die reine und
	angewandte Mathematik, 1987.
	
	\bibitem{calcvar15} Sinestrari, C. {\em Convex hypersurfaces evolving by volume preserving curvature flows.} Calc. Var. 54:1985–1993, Springer, DOI 10.1007/s00526-015-0852-z, 2015 .
	
	\bibitem{mccoy} McCoy, J. {\em The Surface Area Preserving Mean Curvature Flow.} Asian J. Math. Vol. 7, No. 1, pp. 007–030, March 2003.
	
	
	\bibitem{protterweinberger}  Protter, M. H.;  Weinberger, H. F.; {\em Maximum Principles in Differential Equations },  Springer, 1984. 
	
	%\bibitem{LeeRiemannian} Lee, J.M.; {\em Riemannian Manifolds},  Springer Graduate Texts in Mathematics 176, 1997. 
	
	\bibitem{LeeRiemannian2ndEd} Lee, J.M.; {\em Introduction to Riemannian Manifolds, Second Edition},  Springer Graduate Texts in Mathematics 176, 2018. 
	
	\bibitem{Lee} Lee, J.M.; {\em Introduction to Smooth Manifolds, Second Edition},  Springer Graduate Texts in Mathematics 218, 2013. 
	
	\bibitem{Evans} Evans, L.C.; {\em Partial Differential Equations},  American Mathematical Society, 2010. 
	
	\bibitem{Gerhardt Curvature} Gerhardt, C.; {\em Curvature problems}, International Press, 2006.
	
	\bibitem{DoCarmo} Do Carmo, M.P.; {\em Differential Geometry of Curves and Surfaces, Second Edition},  Dover Books on Mathematics, 2016. 
	
	%\bibitem{paper3}  J. Scheuer; {\em Isotropic functions revisited},  Arch. Math. 110, 591–604, 2018.
	
	\bibitem{mantegazza} Mantegazza C. {\em Lecture Notes on Mean Curvature Flow}
	
	%\bibitem{hamilton}  R.S. Hamilton, {\em Three-Manifolds with Positive Ricci Curvature}
	
	\bibitem{tomography} Gardner RJ. {\em Geometric Tomography}. 2nd ed. Cambridge: Cambridge University Press; 2006
	
	
	\bibitem{gilardi} Gilardi, G.; {\em Analisi Matematica di Base},  Second Edition,  McGraw-Hill, 2011. 
\end{thebibliography}
%\include{./TeX_files/ringraziamenti}


\end{document}